Carrier phase and amplitude estimation for phase shift keying using pilots and data

### 2012-08-13 paper.tex
Added to paper.  Started added the empirical proc stuff to the appendix.  Needs more work.  I'm not sure I've got the notation right.

\begin{lemma}\label{lem:supDLlambdan}
If $N$ is finite then $U_L \rightarrow 0$ almost surely as $L \rightarrow \infty$.
\end{lemma}
\begin{IEEEproof}
Put
\[
Z_i(\lambda) = \begin{cases}
R_i\cos(\lambda + \Phi_i) , & i \in P \\
R_i\cos\sfracpart{\lambda + \Phi_i} , & i \in D
\end{cases}
\]
so that
\[
D_L(\lambda) = G_L(\lambda) - T_L(\lambda) = \frac{1}{L}\sum_{i=1}^{L} \big( Z_i(\lambda) - \expect Z_i(\lambda) \big).
\]
Now $Z_1(\lambda_n), \dots,Z_L(\lambda_n)$ are independent with finite variance (because $\expect R_i^2$ is finite), so for each $n =1, \dots, N$,
\[
\abs{D_L(\lambda_n)} = \abs{\frac{1}{L}\sum_{i=1}^{L} \big( Z_i(\lambda_n) - \expect Z_i(\lambda)\big)} \rightarrow 0
\]
almost surely as $L\rightarrow\infty$ by the Kolmogorov's strong law of large numbers~\cite[Theorem 2.3.10]{SenSinger_large_sample_stats_1993}.  Now, since $N$ is finite,
\[
U_L = \sup_{n=1,\dots,N}\sabs{D_L(\lambda_n)} \leq \sum_{n=1}^N \sabs{D_L(\lambda_n)} \rightarrow 0
\]
almost surely to zero as $L \rightarrow \infty$.
\end{IEEEproof}

@@

\begin{lemma}\label{lem:CL} The following statements hold:
\begin{enumerate}
\item $\expect C_L \leq \tfrac{2\pi}{N}\expect R_1$,
\item for any $\epsilon > 0$, $\prob\left\{ \lim_{L \rightarrow \infty} C_L > \epsilon + \tfrac{2\pi}{N}\expect R_1 \right\} = 0$.
\end{enumerate}
\end{lemma}
\begin{IEEEproof}
If $\lambda \in L_n$, then $\lambda = \lambda_n + \delta$ with $\delta < \tfrac{2\pi}{N}$, and from Lemma~\ref{lem:coslipshitz},
\begin{align*}
&\abs{\cos(\lambda + \Phi_i) - \cos(\lambda_n + \Phi_i)} \leq \tfrac{2\pi}{N}, \;\;\; \text{and} \\
&\abs{\cos\sfracpart{\lambda + \Phi_i} - \cos\sfracpart{\lambda_n + \Phi_i}} \leq \tfrac{2\pi}{N}.
\end{align*}
Because this results does not depend on $n$,
\[
\sup_{n=1,\dots,N}\sup_{\lambda \in L_n} \abs{Z_i(\lambda) - Z_i(\lambda_n)} \leq R_i \frac{2\pi}{N}
\]
for all $i = P \cup D$.  Now,
\begin{align*}
C_L &= \sup_{n=1,\dots,N}\sup_{\lambda \in L_n}\abs{\frac{1}{L}\sum_{i=1}^L Z_i(\lambda) - Z_i(\lambda_n)} \\
&\leq \frac{1}{L}\sum_{i=1}^L \sup_{n=1,\dots,N}\sup_{\lambda \in L_n} \abs{Z_i(\lambda) - Z_i(\lambda_n)} \\
&\leq \frac{2\pi}{N L}\sum_{i=1}^L R_i .
\end{align*}
Thus, 
\[
\expect C_L \leq \expect \frac{2\pi}{N L}\sum_{i=1}^L R_i = \tfrac{2\pi}{N}\expect R_1
\]
and the first statement holds.  Now, 
\[
\frac{2\pi}{N L}\sum_{i=1}^L R_i \rightarrow \frac{2\pi}{N}\expect R_1
\] 
almost surely to $\frac{2\pi}{N}\expect R_1$ as $L \rightarrow\infty$ by the strong law of large numbers, and so, for any $\epsilon > 0$,
\begin{align*}
\prob&\left\{ \lim_{L \rightarrow \infty} C_L > \epsilon + \tfrac{2\pi}{N}\expect R_1 \right\} \\
&\leq \prob\left\{ \lim_{L \rightarrow \infty} \frac{2\pi}{N L}\sum_{i=1}^L R_i > \epsilon + \tfrac{2\pi}{N}\expect R_1 \right\} = 0.
\end{align*}
\end{IEEEproof}

@@

\begin{lemma}\label{lem:ZYLempiricproc}
For any $\delta > 0$ and $\nu > 0$, there exists $\epsilon > 0$ such that:
\begin{enumerate}
\item $\Pr\left\{ \sup_{\sabs{\lambda}<\epsilon}\sabs{W_L(\lambda)} > \delta  \right\} < \nu$, and,
\item $\Pr\left\{ \sup_{\sabs{\lambda}<\epsilon}\sabs{Y_L(\lambda)} > \delta  \right\} < \nu$,
\end{enumerate}
for all positive integers $L$
\end{lemma}
\begin{IEEEproof}
These results are related to what is called \emph{tightness} in the literature on empirical processes and weak convergence on metric spaces~\cite{Billingsley1999_convergence_of_probability_measures,Dudley_unif_central_lim_th_1999,Shorak_emp_proc_stat_2009}.  The proof is based on a technique called \emph{symmetrisation} and another technique called \emph{chaining} (also known as \emph{bracketing})~\cite{Pollard_asymp_empi_proc_1989}.  We will only give a proof of the first statement regarding the function $W_L$.  The proof for the second statement regarding $Y_L$ is similar.

Put 
\[
f_i(\lambda, R_i, \Phi_i) = \begin{cases}
R_i( \sin(\lambda + \Phi_i) - \sin(\Phi_i)), & i \in P \\
R_i( \sin\sfracpart{\lambda + \Phi_i} - \sin\sfracpart{\Phi_i}), & i \in D \\
\end{cases}
\]
so that
\[
W_L(\lambda) = \frac{1}{\sqrt{L}} \sum_{i = 1}^{L} \big( f_i(\lambda, R_i, \Phi_i) - \expect f_i(\lambda, R_i, \Phi_i) \big).
\]
Let $\{g_i\}$ be a sequence of independent standard normal random variables, independent of $\{R_i\}$ and $\{\Phi_i\}$.  Lemma~\ref{lem:symmetrisation} shows that
\[
\expect \sup_{\sabs{\lambda} < \epsilon} \abs{ W_L(\lambda)} \leq \sqrt{2\pi} \; \expect \sup_{\sabs{\lambda} < \epsilon}  \abs{ X_L(\lambda) },
\]
where 
\begin{equation}\label{eq:ZpsiCondGaussProc}
X_L(\lambda) = \frac{1}{\sqrt{L}} \sum_{n=1}^{L} g_i f_i(\lambda, R_i, \Phi_i),
\end{equation}
and where $\expect$ runs over all of $\{g_i\}$, $\{R_i\}$ and $\{\Phi_i\}$.  Conditionally on $\{\Phi_i\}$ and $\{R_i\}$, $\{X_L(\lambda), \lambda \in \reals \}$ is a \emph{Gaussian process}, and numerous techniques exist for its analysis.  Lemma~\ref{lem:chaining} shows that for any $\kappa > 0$ there exists $\epsilon > 0$ such that
\[
\expect \sup_{\sabs{\lambda} < \epsilon} \abs{ X_L(\lambda) } < \kappa.
\]
It follows that,
\[
\expect \sup_{\sabs{\lambda} < \epsilon} \abs{ W_L(\lambda)}  <  \sqrt{2\pi} \; \kappa,
\]
and by Markov's inequality,
\[
\prob \cubr{  \sup_{\sabs{\lambda} < \epsilon} \abs{ W_L(\lambda)} > \delta } \leq  \sqrt{2\pi} \; \frac{\kappa}{\delta},
\]
for any $\delta > 0$.  The proof follows by choosing $\nu =  \sqrt{2\pi} \kappa/\delta$.  It remains to prove Lemmas~\ref{lem:symmetrisation}~and~\ref{lem:chaining}.
\end{IEEEproof}

@@

W_L(\lambda) &= \frac{1}{\sqrt{L}} \sum_{i = 1}^{L} \big( f_i(\lambda, R_i, \Phi_i) - \expect_{R,\Phi} f_i(\lambda, R_i', \Phi_i') \big) \\
&= \expect_{R,\Phi} \frac{1}{\sqrt{L}} \sum_{i=1}^{L} ( f_{i} - f_{i}^\prime ),

@@

 \sup_{\sabs{\lambda} < \epsilon} \abs{ W_L(\lambda)} &= \sup_{\sabs{\lambda} < \epsilon}  \abs{\frac{1}{\sqrt{L}} \expect_{R,\Phi} \sum_{i=1}^{L} (f_{i} - f_{i}^\prime )} \\
&\leq \sup_{\sabs{\lambda} < \epsilon} \expect_{R,\Phi}  \abs{ \frac{1}{\sqrt{L}} \sum_{i=1}^{L}  (f_{i} - f_{i}^\prime) },

@@

 \sup_{\sabs{\lambda} < \epsilon} \abs{ W_L(\lambda)} \leq \expect_{R,\Phi} \sup_{\sabs{\lambda} < \epsilon} \abs{ \frac{1}{\sqrt{L}}\sum_{i=1}^{L} ( f_{i} - f_{i}^\prime ) }.

@@

 \expect \sup_{\sabs{\lambda} < \epsilon} \abs{ W_L(\lambda)} \leq  \expect \sup_{\sabs{\lambda} < \epsilon} \abs{ \frac{1}{\sqrt{L}}\sum_{i=1}^{L}  (f_{i} - f_{i}^\prime) },

@@

 \expect \sup_{\sabs{\lambda} < \epsilon}  &\abs{  \frac{1}{\sqrt{L}}\sum_{i=1}^{L}  (f_{i} - f_{i}^\prime) } \\
&= \expect \sup_{\sabs{\lambda} < \epsilon}  \abs{  \frac{1}{\sqrt{L}}\sum_{i=1}^{L} \sigma_i ( f_{i} - f_{i}^\prime) }.

@@

\abs{ \sum_{i=1}^{L} \sigma_i (f_{i} - f_{i}^\prime)} \leq \abs{ \sum_{i=1}^{L} \sigma_i f_{i} } + \abs{ \sum_{i=1}^{L}  \sigma_i f_{i}^\prime },

@@

 \expect \sup_{\sabs{\lambda} < \epsilon} \abs{ W_L(\lambda)} &\leq \expect \sup_{\sabs{\lambda} < \epsilon}  \abs{ \frac{1}{\sqrt{L}}\sum_{i=1}^{L} \sigma_i f_{i} } \\
&\hspace{1cm} + \expect \sup_{\sabs{\lambda} < \epsilon}  \abs{\frac{1}{\sqrt{L}} \sum_{i=1}^{L}  \sigma_i  f_{i}^\prime } \\
&= 2 \; \expect \sup_{\sabs{\lambda} < \epsilon}  \abs{ \frac{1}{\sqrt{L}}\sum_{i=1}^{L} \sigma_i f_{i} }.

@@

\expect \sup_{\sabs{\lambda} < \epsilon}  &\abs{ \frac{1}{\sqrt{L}}\sum_{i=1}^{L} \sigma_i f_{i} } \\
&= \expect \sup_{\sabs{\lambda} < \epsilon}  \abs{ \frac{1}{\sqrt{L}}\sum_{i=1}^{L} \sigma_i f_{i} \sqrt{\frac{\pi}{2}}\expect_{R,\Phi} \abs{g_i}} \\
&\leq \sqrt{\frac{\pi}{2}} \expect \sup_{\sabs{\lambda} < \epsilon}  \abs{ \frac{1}{ \sqrt{L}}\sum_{i=1}^{L} \sigma_i \abs{g_i}  f_{i}},

@@

\expect \sup_{\sabs{\lambda} < \epsilon} \abs{W_L(\lambda)}  &\leq 2\sqrt{\frac{\pi}{2}} \expect \sup_{\sabs{\lambda} < \epsilon}  \abs{ \frac{1}{\sqrt{L}}\sum_{i=1}^{L} g_i  f_{i}} \\

@@

\begin{lemma} \label{lem:chaining}
For any $\kappa > 0$ there exists $\epsilon > 0$ such that
\[
\expect \sup_{\sabs{\lambda} < \epsilon} \abs{ X_L(\lambda) } < \kappa,
\]
where $X_L(\lambda)$ is defined by~\eqref{eq:ZpsiCondGaussProc}.
\end{lemma}
\begin{IEEEproof}

>>>>

\begin{lemma}\label{lem:supDLlambdan}
If $N$ is finite then $U_L \rightarrow 0$ almost surely as $L \rightarrow \infty$.
\end{lemma}
\begin{IEEEproof}
Put
\[
Z_i(\lambda) = \begin{cases}
R_i\cos(\lambda + \Phi_i) , & i \in P \\
R_i\cos\sfracpart{\lambda + \Phi_i} , & i \in D
\end{cases}
\]
so that
\[
D_L(\lambda) = G_L(\lambda) - T_L(\lambda) = \frac{1}{L}\sum_{i\in P \cup D} \big( Z_i(\lambda) - \expect Z_i(\lambda) \big).
\]
Now $Z_1(\lambda_n), \dots,Z_L(\lambda_n)$ are independent with finite variance (because $\expect R_i^2$ is finite), so for each $n =1, \dots, N$,
\[
\abs{D_L(\lambda_n)} = \abs{\frac{1}{L}\sum_{i\in P \cup D} \big( Z_i(\lambda_n) - \expect Z_i(\lambda)\big)} \rightarrow 0
\]
almost surely as $L\rightarrow\infty$ by the Kolmogorov's strong law of large numbers~\cite[Theorem 2.3.10]{SenSinger_large_sample_stats_1993}.  Now, since $N$ is finite,
\[
U_L = \sup_{n=1,\dots,N}\sabs{D_L(\lambda_n)} \leq \sum_{n=1}^N \sabs{D_L(\lambda_n)} \rightarrow 0
\]
almost surely to zero as $L \rightarrow \infty$.
\end{IEEEproof}

@@

\begin{lemma}\label{lem:CL} The following statements hold:
\begin{enumerate}
\item $\expect C_L \leq \tfrac{2\pi}{N}\expect R_1$,
\item for any $\epsilon > 0$, $\prob\left\{ \lim_{L \rightarrow \infty} C_L > \epsilon + \tfrac{2\pi}{N}\expect R_1 \right\} = 0$.
\end{enumerate}
\end{lemma}
\begin{IEEEproof}
If $\lambda \in L_n$, then $\lambda = \lambda_n + \delta$ with $\delta < \tfrac{2\pi}{N}$, and from Lemma~\ref{lem:coslipshitz},
\begin{align*}
&\abs{\cos(\lambda + \Phi_i) - \cos(\lambda_n + \Phi_i)} \leq \tfrac{2\pi}{N}, \;\;\; \text{and} \\
&\abs{\cos\sfracpart{\lambda + \Phi_i} - \cos\sfracpart{\lambda_n + \Phi_i}} \leq \tfrac{2\pi}{N}.
\end{align*}
Because this results does not depend on $n$,
\[
\sup_{n=1,\dots,N}\sup_{\lambda \in L_n} \abs{Z_i(\lambda) - Z_i(\lambda_n)} \leq R_i \frac{2\pi}{N}
\]
for all $i = P \cup D$.  Now,
\begin{align*}
C_L &= \sup_{n=1,\dots,N}\sup_{\lambda \in L_n}\abs{\frac{1}{L}\sum_{i \in P \cup D} Z_i(\lambda) - Z_i(\lambda_n)} \\
&\leq \frac{1}{L}\sum_{i \in P \cup D} \sup_{n=1,\dots,N}\sup_{\lambda \in L_n} \abs{Z_i(\lambda) - Z_i(\lambda_n)} \\
&\leq \frac{2\pi}{N L}\sum_{i \in P \cup D} R_i .
\end{align*}
Thus, 
\[
\expect C_L \leq \expect \frac{2\pi}{N L}\sum_{i \in P \cup D} R_i = \tfrac{2\pi}{N}\expect R_1
\]
and the first statement holds.  Now, 
\[
\frac{2\pi}{N L}\sum_{i \in P \cup D} R_i \rightarrow \frac{2\pi}{N}\expect R_1
\] 
almost surely to $\frac{2\pi}{N}\expect R_1$ as $L \rightarrow\infty$ by the strong law of large numbers, and so, for any $\epsilon > 0$,
\begin{align*}
\prob&\left\{ \lim_{L \rightarrow \infty} C_L > \epsilon + \tfrac{2\pi}{N}\expect R_1 \right\} \\
&\leq \prob\left\{ \lim_{L \rightarrow \infty} \frac{2\pi}{N L}\sum_{i \in P \cup D} R_i > \epsilon + \tfrac{2\pi}{N}\expect R_1 \right\} = 0.
\end{align*}
\end{IEEEproof}

@@

\begin{lemma}\label{lem:ZYLempiricproc}
For any $\delta > 0$ and $\nu > 0$, there exists $\epsilon > 0$ such that:
\begin{enumerate}
\item $\Pr\left\{ \sup_{\sabs{\lambda}<\epsilon}\sabs{W_L(\lambda)} > \delta  \right\} < \nu$, and,
\item $\Pr\left\{ \sup_{\sabs{\lambda}<\epsilon}\sabs{Y_L(\lambda)} > \delta  \right\} < \nu$,
\end{enumerate}
for all positive integers $L$.
\end{lemma}
\begin{IEEEproof}
These results are related to what is called \emph{tightness} in the literature on empirical processes and weak convergence on metric spaces~\cite{Billingsley1999_convergence_of_probability_measures,Dudley_unif_central_lim_th_1999,Shorak_emp_proc_stat_2009}.  The proof is based on a technique called \emph{symmetrisation} and another technique called \emph{chaining} (also known as \emph{bracketing})~\cite{Pollard_asymp_empi_proc_1989}.  We will only give a proof of the first statement regarding the function $W_L$.  The proof for the second statement regarding $Y_L$ is similar.

Put 
\[
f_i(\lambda, R_i, \Phi_i) = \begin{cases}
R_i( \sin(\lambda + \Phi_i) - \sin(\Phi_i)), & i \in P \\
R_i( \sin\sfracpart{\lambda + \Phi_i} - \sin\sfracpart{\Phi_i}), & i \in D \\
\end{cases}
\]
so that
\[
W_L(\lambda) = \frac{1}{\sqrt{L}} \sum_{i \in P \cup D} \big( f_i(\lambda, R_i, \Phi_i) - \expect f_i(\lambda, R_i, \Phi_i) \big).
\]
Let $\{g_i\}$ be a sequence of independent standard normal random variables, independent of $\{R_i\}$ and $\{\Phi_i\}$.  Lemma~\ref{lem:symmetrisation} shows that
\[
\expect \sup_{\sabs{\lambda} < \epsilon} \abs{ W_L(\lambda)} \leq \sqrt{2\pi} \; \expect \sup_{\sabs{\lambda} < \epsilon}  \abs{ X_L(\lambda) },
\]
where 
\begin{equation}\label{eq:ZpsiCondGaussProc}
X_L(\lambda) = \frac{1}{\sqrt{L}} \sum_{i \in P \cup D} g_i f_i(\lambda, R_i, \Phi_i),
\end{equation}
and where $\expect$ runs over all of $\{g_i\}$, $\{R_i\}$ and $\{\Phi_i\}$.  Conditionally on $\{\Phi_i\}$ and $\{R_i\}$, $\{X_L(\lambda), \lambda \in \reals \}$ is a \emph{Gaussian process}, and numerous techniques exist for its analysis.  Lemma~\ref{lem:chaining} shows that for any $\kappa > 0$ there exists $\epsilon > 0$ such that
\[
\expect \sup_{\sabs{\lambda} < \epsilon} \abs{ X_L(\lambda) } < \kappa.
\]
It follows that,
\[
\expect \sup_{\sabs{\lambda} < \epsilon} \abs{ W_L(\lambda)}  <  \sqrt{2\pi} \; \kappa,
\]
and by Markov's inequality,
\[
\prob \cubr{  \sup_{\sabs{\lambda} < \epsilon} \abs{ W_L(\lambda)} > \delta } \leq  \sqrt{2\pi} \; \frac{\kappa}{\delta},
\]
for any $\delta > 0$.  The proof follows by choosing $\nu =  \sqrt{2\pi} \kappa/\delta$.  It remains to prove Lemmas~\ref{lem:symmetrisation}~and~\ref{lem:chaining}.
\end{IEEEproof}

@@

W_L(\lambda) &= \frac{1}{\sqrt{L}} \sum_{i \in P \cup D} \big( f_i(\lambda, R_i, \Phi_i) - \expect_{R,\Phi} f_i(\lambda, R_i', \Phi_i') \big) \\
&= \expect_{R,\Phi} \frac{1}{\sqrt{L}} \sum_{i \in P \cup D} ( f_{i} - f_{i}^\prime ),

@@

 \sup_{\sabs{\lambda} < \epsilon} \abs{ W_L(\lambda)} &= \sup_{\sabs{\lambda} < \epsilon}  \abs{\frac{1}{\sqrt{L}} \expect_{R,\Phi} \sum_{i \in P \cup D} (f_{i} - f_{i}^\prime )} \\
&\leq \sup_{\sabs{\lambda} < \epsilon} \expect_{R,\Phi}  \abs{ \frac{1}{\sqrt{L}} \sum_{i \in P \cup D}  (f_{i} - f_{i}^\prime) },

@@

 \sup_{\sabs{\lambda} < \epsilon} \abs{ W_L(\lambda)} \leq \expect_{R,\Phi} \sup_{\sabs{\lambda} < \epsilon} \abs{ \frac{1}{\sqrt{L}}\sum_{i \in P \cup D} ( f_{i} - f_{i}^\prime ) }.

@@

 \expect \sup_{\sabs{\lambda} < \epsilon} \abs{ W_L(\lambda)} \leq  \expect \sup_{\sabs{\lambda} < \epsilon} \abs{ \frac{1}{\sqrt{L}}\sum_{i \in P \cup D} (f_{i} - f_{i}^\prime) },

@@

 \expect \sup_{\sabs{\lambda} < \epsilon}  &\abs{  \frac{1}{\sqrt{L}}\sum_{i \in P \cup D}  (f_{i} - f_{i}^\prime) } \\
&= \expect \sup_{\sabs{\lambda} < \epsilon}  \abs{  \frac{1}{\sqrt{L}}\sum_{i \in P \cup D} \sigma_i ( f_{i} - f_{i}^\prime) }.

@@

\abs{ \sum_{i\in P \cup D} \sigma_i (f_{i} - f_{i}^\prime)} \leq \abs{ \sum_{i \in P \cup D} \sigma_i f_{i} } + \abs{ \sum_{i\in P \cup D}  \sigma_i f_{i}^\prime },

@@

 \expect \sup_{\sabs{\lambda} < \epsilon} \abs{ W_L(\lambda)} &\leq \expect \sup_{\sabs{\lambda} < \epsilon}  \abs{ \frac{1}{\sqrt{L}}\sum_{i\in P \cup D} \sigma_i f_{i} } \\
&\hspace{1cm} + \expect \sup_{\sabs{\lambda} < \epsilon}  \abs{\frac{1}{\sqrt{L}} \sum_{i \in P \cup D}  \sigma_i  f_{i}^\prime } \\
&= 2 \; \expect \sup_{\sabs{\lambda} < \epsilon}  \abs{ \frac{1}{\sqrt{L}}\sum_{i \in P \cup D} \sigma_i f_{i} }.

@@

\expect \sup_{\sabs{\lambda} < \epsilon}  &\abs{ \frac{1}{\sqrt{L}}\sum_{i \in P \cup D} \sigma_i f_{i} } \\
&= \expect \sup_{\sabs{\lambda} < \epsilon}  \abs{ \frac{1}{\sqrt{L}}\sum_{i \in P \cup D} \sigma_i f_{i} \sqrt{\frac{\pi}{2}}\expect_{R,\Phi} \abs{g_i}} \\
&\leq \sqrt{\frac{\pi}{2}} \expect \sup_{\sabs{\lambda} < \epsilon}  \abs{ \frac{1}{ \sqrt{L}}\sum_{i \in P \cup D} \sigma_i \abs{g_i}  f_{i}},

@@

\expect \sup_{\sabs{\lambda} < \epsilon} \abs{W_L(\lambda)}  &\leq 2\sqrt{\frac{\pi}{2}} \expect \sup_{\sabs{\lambda} < \epsilon}  \abs{ \frac{1}{\sqrt{L}}\sum_{i\in P \cup D} g_i  f_{i}} \\

@@

\begin{lemma} \label{lem:chaining}
For any $\kappa > 0$ there exists $\epsilon > 0$ such that
\[
\expect \sup_{\sabs{\lambda} < \epsilon} \abs{ X_L(\lambda) } < \kappa,
\]
where $X_L(\lambda)$ is defined by~\eqref{eq:ZpsiCondGaussProc}.
\end{lemma}
\begin{IEEEproof}
Without loss of generality, assume that $\epsilon < \tfrac{\pi}{M}$.  Lemma~\ref{lem:chaining2} shows that
\begin{equation}\label{eq:supZCK1} 
\expect_{R,\Phi} \sup_{\sabs{\lambda} < \epsilon} \abs{ X_L(\psibf) } \leq K_1 \sqrt{C_\epsilon(\{\Phi\})}
\end{equation}
where $K_1$ is a finite, positive constant, and $C_\epsilon(\{\Phi\})$ is average number of times $\Phi_i, i \in D$ are inside the set
\[
S_\epsilon = \bigcup_{k \in \ints} [\psi_k - \epsilon, \psi_k + \epsilon],
\]
where $\psi_k = \tfrac{2\pi}{M}k + \tfrac{\pi}{M}$.  That is,
\[
C_\epsilon(\{\Phi\}) = \frac{1}{L} \sum_{i \in P \cup D} I_\epsilon(\Phi_i)
\]
where $I_\epsilon(\Phi_i) = 1$ if $\Phi_i \in S_\epsilon$ and zero otherwise.
\end{IEEEproof}

The proofs of Lemmas~\ref{lem:chaining2}~and~\ref{lem:chaining3} are based on a technique called \emph{chaining} (or \emph{bracketing})~\cite{Dudley_unif_central_lim_th_1999,Ossiander_clt_bracketing_1984,Pollard_asymp_empi_proc_1989,Pollard_new_ways_clts_1986}.  The proofs here follow those of Pollard~\cite[Section 3]{Pollard_asymp_empi_proc_1989}.  %Within the remaining proofs, we are interested in expectations conditional on the phase noise sequence $\{\Phi_n\}$, so for the purpose of these lemmas, $\{\Phi_n\}$ is treated as a fixed realisation.  
For notational convenience we use the abbreviations 
\[
C_\epsilon = C_\epsilon(\{\Phi\}) \qquad \text{and} \qquad f_{i}(\lambda) = f_{i}(\lambda, R_i, \Phi_i)
\]
in what follows.  As in Lemma~\ref{lem:chaining} we assume, without loss of generality, that $\epsilon < \tfrac{1}{m+1}$.  %This comes at no loss since Lemma~\ref{lem:chaining} only asks for the existence of an $\epsilon > 0$.

\begin{lemma}\label{lem:chaining2}
There exists a positive constant $K_1$ such that
\[
\expect_{R,\Phi} \sup_{\sabs{\lambda} < \epsilon} \abs{ X_L(\lambda) } \leq K_1 \sqrt{C_\epsilon}.
\]
\end{lemma}
\begin{IEEEproof}
Let $B_\epsilon = \{x \in \reals \mid \abs{x} < \epsilon\}$ be the set of real numbers with magnitude less than $\epsilon$.  For each non negative integer $k$, let $T_\epsilon(k)$ be a discrete subset of $\reals$ with the property that for every $\lambda \in B_\epsilon$ there exists $\lambda^* \in T_\epsilon(k)$ such that the pseudometric
\[
d(\lambda, \lambda^*) = \sum_{i \in P \cup D} \big( f_{i}(\lambda) - f_{i}(\lambda^*) \big)^2 \leq 2^{-k} C_\epsilon N.
\]
We specifically define $T_\epsilon(0)$ to contain only zero.  Defined this way 
\end{IEEEproof}

\begin{lemma}
Suppose $\sabs{\lambda} < \epsilon$ and $\sabs{\lambda^*} < \epsilon$ with $\epsilon < \tfrac{\pi}{M}$. Then
\begin{align*}
d(\lambda, \lambda^*) &= \sum_{i \in P \cup D} \big( f_{i}(\lambda) - f_{i}(\lambda^*) \big)^2 \\
&\leq R_i^2 L \left( (\lambda - \lambda^*)^2 + 4 C_\epsilon \right).
\end{align*}
\end{lemma}

\begin{lemma}
If $i \in P$, then $\big(f_{i}(\lambda) - f_{i}(\lambda^*)\big)^2 \leq R_i^2(\lambda - \lambda^*)^2.$
\end{lemma}
\begin{IEEEproof} 
We have
\[
\big(f_{i}(\lambda) - f_{i}(\lambda^*)\big)^2 = R_i^2\sabs{\sin(\lambda + \Phi_i) - \sin(\lambda^* + \Phi_i)}^2
\]
and, since $\sin(\cdot)$ is Lipshitz continuous with constant $K=1$,
\[
\sabs{\sin(\lambda + \Phi_i) - \sin(\lambda^* + \Phi_i)} \leq K\sabs{\lambda - \lambda^*} = \sabs{\lambda - \lambda^*}.
\]
\end{IEEEproof}

\begin{lemma}
Suppose $\sabs{\lambda} < \epsilon$ and $\sabs{\lambda^*} < \epsilon$ with $\epsilon < \tfrac{\pi}{M}$.  If $i \in D$, then
\begin{equation}\label{eq:fismall}
\big(f_{i}(\lambda) - f_{i}(\lambda^*)\big)^2 \leq R_i^2(\lambda - \lambda^*)^2
\end{equation}
when $\Phi_i \notin S_\epsilon$, otherwise,
\begin{equation}\label{eq:fibig}
\big(f_{i}(\lambda) - f_{i}(\lambda^*)\big)^2 \leq 4 R_i^2.
\end{equation}
\end{lemma}
\begin{IEEEproof}
Because $\sin(\cdot) \leq 1$ it follows that
\begin{align*}
\big(f_{i}(\lambda) - f_{i}(\lambda^*)\big)^2 &= R_i^2\sabs{\sin\fracpart{\lambda + \Phi_i} - \sin\fracpart{\lambda^* + \Phi_i}}^2 \\
&\leq 4 R_i^2
\end{align*}
for any $\Phi_i \in \reals$, and so~\eqref{eq:fibig} holds.  If $\Phi_i \notin S_\epsilon$ then $\Phi_i \in (\psi_{k-1} + \epsilon, \psi_{k} - \epsilon)$ for some $k\in\ints$ and 
\[
\fracpart{\Phi_i + \lambda} = \Phi_i + \lambda - \tfrac{2\pi}{M}k
\] 
and
\[
\fracpart{\Phi_i + \lambda^*} = \Phi_i + \lambda^* - \tfrac{2\pi}{M}k 
\]
and, since $\sin(\cdot)$ is Lipshitz continuous with constant $K=1$,
\begin{align*}
\vert \sin&\fracpart{\Phi_i + \lambda} - \sin\fracpart{\Phi_i + \lambda^*}\vert \\
&=  \sabs{\sin(\Phi_i + \lambda - \tfrac{2\pi}{M}k) - \sin(\Phi_i + \lambda^* - \tfrac{2\pi}{M}k)} \\
&\leq K \sabs{\lambda - \lambda^*} \\
&= \sabs{\lambda - \lambda^*}.
\end{align*}
Thus~\eqref{eq:fismall} holds. 
\end{IEEEproof}

\begin{lemma}\label{lem:chaining3}(Chaining)
For all positive integers $k$,
\[
\expect_{R,\Phi} \sup_{\psibf \in T_\epsilon(k) } \abs{ X_L(\lambda) } \leq \sqrt{C_\epsilon} \sum_{i=1}^{k}\frac{?}{2^{i/2}}.
\]
\end{lemma}
\begin{IEEEproof}
